Modelling state-switching behaviour in functional data with hidden Markov models

### 2020-08-31 Report/Sections/results.tex

The HHMM-DFT, which ignores auto-correlation in acceleration, decodes dive types and subdive states similarly to the CarHHMM-DFT, but it is less likely to categorize the behaviour at the beginning and end of dives as subdive type 3. In addition, the HHMM-DFT produces estimates of $\sigma_A^{*(1)}$, $\sigma_A^{*(2)}$, and $\sigma_A^{*(3)}$ which are approximately $50$ to $100$ percent larger than those of the CarHHMM-DFT for all axes of acceleration. The estimated uncertainties of the estimates of $\mu_A^{*(1)}$, $\mu_A^{*(2)}$, and $\mu_A^{*(3)}$ are also less than half of those for the CarHHMM-DFT for all axes of acceleration. Further, the empirical auto-correlation of acceleration within each decoded subdive state was at least 0.5 for all acceleration axes and subdive states, and the pseudoresiduals of the HHMM-DFT contain several outliers. These findings suggest that the HHMM-DFT is a significantly worse fit to this data than the full CarHHMM-DFT.

>>>>

The HHMM-DFT, which ignores auto-correlation in acceleration, decodes dive types and subdive states similarly to the CarHHMM-DFT, but it is less likely to categorize the behaviour at the beginning and end of dives as subdive type 3. In addition, the HHMM-DFT produces estimates of $\sigma_A^{*(\cdot,1)}$, $\sigma_A^{*(\cdot,2)}$, and $\sigma_A^{*(\cdot,3)}$ which are approximately $50$ to $100$ percent larger than those of the CarHHMM-DFT for all axes of acceleration. The estimated uncertainties of the estimates of $\mu_A^{*(\cdot,1)}$, $\mu_A^{*(\cdot,2)}$, and $\mu_A^{*(\cdot,3)}$ are also less than half of those for the CarHHMM-DFT for all axes of acceleration. Further, the empirical auto-correlation of acceleration within each decoded subdive state was at least 0.5 for all acceleration axes and subdive states, and the pseudoresiduals of the HHMM-DFT contain several outliers. These findings suggest that the HHMM-DFT is a significantly worse fit to this data than the full CarHHMM-DFT.
